Market Simulator

### 2020-08-07 analysis/05_market_simulator.Rmd
Valueboxes taken out

Organization Breakdown {.tabset .tabset-fade}
--------------------------------------------------
### Amnesty International Market Share

@@

```{r valuebox ai}
renderValueBox({
  choice = df()

  persona = p_beta1 # Choose the persona

  valueBox(ai_rate,
           color = "#FFC30B",
           icon = "fa-percent")
})
```

@@

### Greenpeace Market Share

@@

```{r valuebox gp}
renderValueBox({
  choice = df()
  persona = p_beta1 # Choose the persona

  valueBox(gp_rate,
           color = "#3fad48",
           icon = "fa-percent")
})
```

@@

### Oxfam Market Share

@@

```{r valuebox ox}
renderValueBox({
  choice = df()

  persona = p_beta1 # Choose the persona

  valueBox(ox_rate,
           color = "#006633",
           icon = "fa-percent")
})
```

@@

### Redcross Market Share

@@

```{r valuebox rc}
renderValueBox({
  choice = df()

  persona = p_beta1 # Choose the persona

  valueBox(rc_rate,
           color = "#660000",
           icon = "fa-percent")
})
```

>>>>

Organization Breakdown {.tabset .tabset-fade}
--------------------------------------------------
### Amnesty International

@@

```{r valuebox ai}
# renderValueBox({
#   choice = df()
#   
#   persona = p_beta1 # Choose the persona
#   
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
#   
#   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   valueBox(ai_rate,
#            color = "#FFC30B",
#            icon = "fa-percent")
# })
```

@@

### Greenpeace

@@

```{r valuebox gp}
# renderValueBox({
#   choice = df()
#   persona = p_beta1 # Choose the persona
#   
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
#   
#   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   valueBox(gp_rate,
#            color = "#3fad48",
#            icon = "fa-percent")
# })
```

@@

### Oxfam

@@

```{r valuebox ox}
# renderValueBox({
#   choice = df()
#   
#   persona = p_beta1 # Choose the persona
#   
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
#   
#   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   valueBox(ox_rate,
#            color = "#006633",
#            icon = "fa-percent")
# })
```

@@

### Redcross

@@

```{r valuebox rc}
# renderValueBox({
#   choice = df()
#   
#   persona = p_beta1 # Choose the persona
#    
#   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2)
#   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2)
#   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2)
#   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2)
#   
#   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
#   
#   valueBox(rc_rate,
#            color = "#660000",
#            icon = "fa-percent")
# })
```
